---
title: "individual2"
author: "Nick Cory"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
choco <- read.csv("https://raw.githubusercontent.com/xdaiISU/ds202materials/master/hwlabs/data/choco.csv") 
str(choco) 
head(choco)
```

## Searching for Best Chocolate
#### 1
```{r}
choco_ratings <- choco$Rating
hist(choco_ratings)
boxplot(choco_ratings)
```

#### 2
```{r}
choco_loc <- choco$Location
barplot(table(choco_loc), las = 2, cex.names = .5)
```



#### 3
```{r}
choco_per <- choco$Cocoa_Percent
plot(choco_ratings, choco_per)
boxplot(choco_ratings~choco_per)
cor(choco_ratings, choco_per)
summary(lm(Rating~Cocoa_Percent, data=choco))
```
```{r}

```


#### 4
```{r}
library(ggplot2)
ratings = choco[order(ave(choco$Rating), decreasing= TRUE), ]
ggplot(ratings, aes(x = Bean_Origin, y = Rating)) + geom_count()+theme(axis.text.x = element_text(angle = 90))
```

Plot is difficult to get values from, will use less values to make more clear. I have experimented with 5 different values to see which can provide important information without overloading the user with unneeded data points. Instead could also use a box plot to make eaiser to read. 

```{r}
boxplot(Rating ~ Bean_Origin, data = choco)
```

```{r}
ratings1 = choco[order(ave(choco$Rating), decreasing= TRUE), ]
ratings1 = ratings[1:100, ]
ggplot(ratings1, aes(x = Bean_Origin, y = Rating)) + geom_count()+theme(axis.text.x = element_text(angle = 90))
```

```{r}
ratings2 = choco[order(ave(choco$Rating), decreasing= TRUE), ]
ratings2 = ratings[1:75, ]
ggplot(ratings2, aes(x = Bean_Origin, y = Rating)) + geom_count()+theme(axis.text.x = element_text(angle = 90))
```

```{r}
ratings3 = choco[order(ave(choco$Rating), decreasing= TRUE), ]
ratings3 = ratings[1:50, ]
ggplot(ratings3, aes(x = Bean_Origin, y = Rating)) + geom_count()+theme(axis.text.x = element_text(angle = 90))
```

```{r}
ratings4 = choco[order(ave(choco$Rating), decreasing= TRUE), ]
ratings4 = ratings[1:25, ]
ggplot(ratings4, aes(x = Bean_Origin, y = Rating)) + geom_count()+theme(axis.text.x = element_text(angle = 90))
```

```{r}
ratings5 = choco[order(ave(choco$Rating), decreasing= TRUE), ]
ratings5 = ratings[1:10, ]
ggplot(ratings5, aes(x = Bean_Origin, y = Rating)) + geom_count()+theme(axis.text.x = element_text(angle = 90))
```

#### 5
1: Find best and worst average ratings to know which products to buy and avoid
2: 


```{r}
Bean_Origin <- choco$Bean_Origin
Cocoa_Percent <- choco$Cocoa_Percent
cocoa = choco[order(ave(Cocoa_Percent), decreasing = TRUE), ]
ggplot(cocoa, aes(x=Cocoa_Percent, y=Bean_Origin))+geom_count()+theme(axis.text.x = element_text(angle=90))

```
